---
title: "Synchrony in vervets"
output: html_notebook
---


## Introduction

This is the code used in the publication "Using synchrony to identify drivers of social network dynamics."

Outline:
1. Get the network strength data
1.2. Fit a multivariate model (accounting for shared events/interactions)
1.3. Fit a multivariate model (accounting for shared events/interactions + Season)
1.4. Fit a multivariate model (accounting for shared events/interactions + Season + NDVI)
2. Get the network modularity data
2.2. Fit a multivariate model (accounting for shared events/interactions)
2.3. Fit a multivariate model (accounting for shared events/interactions + Season)
2.4. Fit a multivariate model (accounting for shared events/interactions + Season + NDVI)
3. Generate plots and tables


load libraries
```{r}
library(dplyr)
library(lubridate)
library(ggplot2)
#devtools::install_github("tbonne/netTS")
library(netTS)
library(igraph)
library(rEDM)
library(brms)
```

## 1. Get the strength data

```{r}
#get the strength data
str.tot.ndvi.ite <- read.csv("network_strength_env.csv")
```

### 1.2 Strength base model

This model accounts for inflation of synchrony due to sampling effort, demographics, number of ITEs, and number of males.

```{r base model}

#scale variables
str.tot.ndvi.ite$size_PTs <- as.vector(str.tot.ndvi.ite$size_PT)
str.tot.ndvi.ite$size_RBMs <- as.vector(str.tot.ndvi.ite$size_RBM)
str.tot.ndvi.ite$size_RSTs <- as.vector(str.tot.ndvi.ite$size_RST)

#build the model formulas
bf_pt <- bf(pts ~ pt.samp.s + ite_pt_rst.s+ite_pt_rbm.s+males_PT.s+ size_PTs+ s(rowID, bs="gp") ) + student()
bf_rbm <- bf(rbms ~ rbm.samp.s+ ite_rbm_rst.s+ite_pt_rbm.s + males_RBM.s+size_RBMs+ s(rowID, bs="gp"))+ student()
bf_rst <- bf(rsts ~ rst.samp.s+ite_rbm_rst.s+ite_pt_rst.s+ males_RST.s+size_RSTs+ s(rowID, bs="gp"))+ student()

#fit the model
fitgp.synch.samp.pop.ite.males <- brm(bf_pt+bf_rbm+bf_rst+ set_rescor(TRUE),
                       data = str.tot.ndvi.ite, iter=2000, chains=4, cores=4,control = list(adapt_delta = 0.99, max_treedepth=12),
                       prior = prior("normal(0,1)", class="b",resp="pts") +
                         prior("normal(0,1)", class="b",resp="rbms")+
                         prior("normal(0,1)", class="b",resp="rsts")+
                       prior("normal(0,1)", class="Intercept",resp="pts") +
                         prior("normal(0,1)", class="Intercept",resp="rbms")+
                         prior("normal(0,1)", class="Intercept",resp="rsts")
                       )

#take a look
summary(fitgp.synch.samp.pop.ite.males)
```


### 1.2 Strength base model + Season

run the seasonal model
```{r strength based model and season}

#build the model formulas
bf_pt <- bf(pts ~ pt.samp.s + size_PTs + s(yday.s,bs="cc")+ ite_pt_rst.s+ite_pt_rbm.s+males_PT.s+ s(rowID, bs="gp") ) + student() #gaussian() s(rowID, bs="gp")
bf_rbm <- bf(rbms ~ rbm.samp.s + size_RBMs + s(yday.s,bs="cc")+ ite_rbm_rst.s+ite_pt_rbm.s + males_RBM.s+ s(rowID, bs="gp"))+ student() # gaussian()
bf_rst <- bf(rsts ~ rst.samp.s + size_RSTs + s(yday.s,bs="cc")+ ite_rbm_rst.s+ite_pt_rst.s + males_RST.s+ s(rowID, bs="gp"))+ student() # gaussian()

#fit the model
fitgp.synch.samp.pop.ite.males.season <- brm(bf_pt+bf_rbm+bf_rst+ set_rescor(TRUE),
                       data = str.tot.ndvi.ite, iter=2000, chains=4, cores=4,control = list(adapt_delta = 0.99, max_treedepth=12),
                       prior = prior("normal(0,1)", class="b",resp="pts") +
                         prior("normal(0,1)", class="b",resp="rbms")+
                         prior("normal(0,1)", class="b",resp="rsts")+
                       prior("normal(0,1)", class="Intercept",resp="pts") +
                         prior("normal(0,1)", class="Intercept",resp="rbms")+
                         prior("normal(0,1)", class="Intercept",resp="rsts")
                       )

#take a look
summary(fitgp.synch.samp.pop.ite.males.season)
```

## run the Strength base + seasons + ndvi

run the ndvi model
```{r strength based model, season, and NDVI}

#build the model formulas
bf_pt <- bf(pts ~ pt.samp.s + size_PTs+ ite_pt_rst.s+ite_pt_rbm.s+males_PT.s + s(yday.s,bs="cc")+ ndvi.s+ s(rowID, bs="gp")) + student() 
bf_rbm <- bf(rbms ~ rbm.samp.s+ size_RBMs+ ite_rbm_rst.s+ite_pt_rbm.s + males_RBM.s+ s(yday.s,bs="cc")+ ndvi.s+ s(rowID, bs="gp"))+ student() 
bf_rst <- bf(rsts ~ rst.samp.s+ size_RSTs+ ite_rbm_rst.s+ite_pt_rst.s + males_RST.s+ s(yday.s,bs="cc")+ ndvi.s+ s(rowID, bs="gp"))+ student() 

#fit the model
fitgp.synch.samp.pop.ite.males.season.ndvi <- brm(bf_pt+bf_rbm+bf_rst+ set_rescor(TRUE),
                       data = str.tot.ndvi.ite, iter=2000, chains=4, cores=4,control = list(adapt_delta = 0.99, max_treedepth = 12),
                       prior = prior("normal(0,1)", class="b",resp="pts") +
                         prior("normal(0,1)", class="b",resp="rbms")+
                         prior("normal(0,1)", class="b",resp="rsts")+
                       prior("normal(0,1)", class="Intercept",resp="pts") +
                         prior("normal(0,1)", class="Intercept",resp="rbms")+
                         prior("normal(0,1)", class="Intercept",resp="rsts")
                       )

#take a look
summary(fitgp.synch.samp.pop.ite.males.season.ndvi)
```


# 2) run model to estimate the synchrony between the groups - Modularity

Get the data
```{r input data}
mod.tot.ite.ndvi<-read.csv("network_modularity_env.csv")
```

### 2.1 Modularity base model

```{r modularity base model}

#build the model functions
bf_pt <- bf(pts ~ pt.samp.s +size_PT.s+ males_PT.s + ite_pt_rbm.s + ite_pt_rst.s + s(rowID, bs="gp") ) + student()
bf_rbm <- bf(rbms ~ rbm.samp.s +size_RBM.s+ males_RBM.s + ite_pt_rbm.s + ite_rbm_rst.s + s(rowID, bs="gp"))+ student()
bf_rst <- bf(rsts ~ rst.samp.s+size_RST.s+ males_RST.s + ite_pt_rst.s + ite_rbm_rst.s + s(rowID, bs="gp"))+ student()

#fit the model
fit.synch.mod.samp.pop.males.ite <- brm(bf_pt+bf_rbm+bf_rst+ set_rescor(TRUE),
                       data = mod.tot.ite.ndvi, iter=2000, chains=4, cores=4,control = list(adapt_delta = 0.95),
                       prior = prior("normal(0,1)", class="b",resp="pts") +
                         prior("normal(0,1)", class="b",resp="rbms")+
                         prior("normal(0,1)", class="b",resp="rsts")+
                       prior("normal(0,1)", class="Intercept",resp="pts") +
                         prior("normal(0,1)", class="Intercept",resp="rbms")+
                         prior("normal(0,1)", class="Intercept",resp="rsts")
                       )

#take a look
summary(fit.synch.mod.samp.pop.males.ite)
```

### 2.3 Modularity base model + season

```{r Modularity season model}


#build model formulas
bf_pt <- bf(pts ~ pt.samp.s +size_PT.s+ males_PT.s + ite_pt_rbm.s + ite_pt_rst.s + s(yday.s,bs="cc")+ s(rowID, bs="gp") ) + student()
bf_rbm <- bf(rbms ~ rbm.samp.s +size_RBM.s+ males_RBM.s + ite_pt_rbm.s + ite_rbm_rst.s + s(yday.s,bs="cc")+ s(rowID, bs="gp"))+ student()
bf_rst <- bf(rsts ~ rst.samp.s+size_RST.s+ males_RST.s + ite_pt_rst.s + ite_rbm_rst.s + s(yday.s,bs="cc")+ s(rowID, bs="gp"))+ student()

#fit the model
fit.synch.mod.samp.pop.males.ite.season <- brm(bf_pt+bf_rbm+bf_rst+ set_rescor(TRUE),
                       data = mod.tot.ite.ndvi, iter=2000, chains=4, cores=4,control = list(adapt_delta = 0.95),
                       prior = prior("normal(0,1)", class="b",resp="pts") +
                         prior("normal(0,1)", class="b",resp="rbms")+
                         prior("normal(0,1)", class="b",resp="rsts")+
                       prior("normal(0,1)", class="Intercept",resp="pts") +
                         prior("normal(0,1)", class="Intercept",resp="rbms")+
                         prior("normal(0,1)", class="Intercept",resp="rsts")
                       )

#take a look
summary(fit.synch.mod.samp.pop.males.ite.season)
```


### 2.3 Modularity base model + season + ndvi

run the ndvi model
```{r modularity based season ndvi}

#build the model formulas
bf_pt <- bf(pts ~ pt.samp.s +size_PT.s+ males_PT.s + ite_pt_rbm.s + ite_pt_rst.s + s(yday.s,bs="cc")+ s(rowID, bs="gp")+ ndvi.s) + student()
bf_rbm <- bf(rbms ~ rbm.samp.s +size_RBM.s+ males_RBM.s + ite_pt_rbm.s + ite_rbm_rst.s + s(yday.s,bs="cc")+ ndvi.s+ s(rowID, bs="gp"))+ student()
bf_rst <- bf(rsts ~ rst.samp.s+size_RST.s+ males_RST.s + ite_pt_rst.s + ite_rbm_rst.s + s(yday.s,bs="cc")+ ndvi.s+ s(rowID, bs="gp"))+ student()

#fit the model
fit.synch.mod.samp.pop.males.ite.season.ndvi <- brm(bf_pt+bf_rbm+bf_rst+ set_rescor(TRUE),
                       data = mod.tot.ite.ndvi, iter=2000, chains=4, cores=4,control = list(adapt_delta = 0.95),
                       prior = prior("normal(0,1)", class="b",resp="pts") +
                         prior("normal(0,1)", class="b",resp="rbms")+
                         prior("normal(0,1)", class="b",resp="rsts")+
                       prior("normal(0,1)", class="Intercept",resp="pts") +
                         prior("normal(0,1)", class="Intercept",resp="rbms")+
                         prior("normal(0,1)", class="Intercept",resp="rsts")
                       )

#take a look
summary(fit.synch.mod.samp.pop.males.ite.season.ndvi)
```


## 3. Plots and tables for the MS

### 3.1 Plot of the change in synchrony

Make a desity ridge plot
```{r synchrony in modularity}

##### basic
post.groom<- as.data.frame(fit.synch.mod.samp.pop.males.ite)

df.cor <- data.frame(cor_pt_rbm = post.groom$rescor__pts__rbms,
                     cor_pt_rst = post.groom$rescor__pts__rsts,
                     cor_rbm_rst = post.groom$rescor__rbms__rsts
)

df.cor$model <- "Base"


#### samp_size_ite_males_season
post.groom<- as.data.frame(fit.synch.mod.samp.pop.males.ite.season)

df.cor.temp <- data.frame(cor_pt_rbm = post.groom$rescor__pts__rbms,
                     cor_pt_rst = post.groom$rescor__pts__rsts,
                     cor_rbm_rst = post.groom$rescor__rbms__rsts
)

df.cor.temp$model <- "+ Season"

df.cor <- bind_rows(df.cor, df.cor.temp)

###full model
post.groom<- as.data.frame(fit.synch.mod.samp.pop.males.ite.season.ndvi)

df.cor.temp <- data.frame(cor_pt_rbm = post.groom$rescor__pts__rbms,
                     cor_pt_rst = post.groom$rescor__pts__rsts,
                     cor_rbm_rst = post.groom$rescor__rbms__rsts
)

df.cor.temp$model <- "+ NDVI"

df.cor <- bind_rows(df.cor, df.cor.temp)



######plot
library(tidyverse)
#df.cor.melt.g <- df.cor %>% gather("troops","groom",-model)
#ggplot(df.cor.melt.g, aes(x=troops, color=model,y=groom)) + geom_violin(aes(fill=model),alpha=0.3, color="black",draw_quantiles=c(0.025,0.5,0.975)) + geom_hline(yintercept = 0, linetype="dashed") + theme_classic()

df.cor.melt.g <- df.cor %>% pivot_longer(!last_col())
names(df.cor.melt.g) <- c("model","troops","value")

library(ggridges)
p.synch.groom.mod <- ggplot(df.cor.melt.g %>% filter(model=="+ NDVI" | model=="+ Season" | model=="Base") , aes(y=factor(model,level=c('+ NDVI','+ Season','Base'   ) ),color=model,x=value)) + geom_density_ridges(aes(fill=model),alpha=0.73, color="black",scale = 4,rel_min_height = 0.01) + geom_hline(yintercept = 0, linetype="dashed") + theme_classic()

library("RColorBrewer")
p.synch.groom.mod<-p.synch.groom.mod + xlim(-1,1) + geom_vline(xintercept = 0, linetype="dashed") + theme(text = element_text(size = 16)) + facet_grid(vars(troops))+ theme(axis.text.y = element_text(hjust = 0)) + labs(y='')

p.synch.groom.mod

```

Make a desity ridge plot
```{r synchrony in modularity}



##### basic
post.groom<- as.data.frame(fitgp.synch.samp.pop.ite.males)

df.cor <- data.frame(cor_pt_rbm = post.groom$rescor__pts__rbms,
                     cor_pt_rst = post.groom$rescor__pts__rsts,
                     cor_rbm_rst = post.groom$rescor__rbms__rsts
)

df.cor$model <- "Base"


#### samp_size_ite_males_season
post.groom<- as.data.frame(fitgp.synch.samp.pop.ite.males.season)

df.cor.temp <- data.frame(cor_pt_rbm = post.groom$rescor__pts__rbms,
                     cor_pt_rst = post.groom$rescor__pts__rsts,
                     cor_rbm_rst = post.groom$rescor__rbms__rsts
)

df.cor.temp$model <- "+ Season"

df.cor <- bind_rows(df.cor, df.cor.temp)

###full model
post.groom<- as.data.frame(fitgp.synch.samp.pop.ite.males.season.ndvi)

df.cor.temp <- data.frame(cor_pt_rbm = post.groom$rescor__pts__rbms,
                     cor_pt_rst = post.groom$rescor__pts__rsts,
                     cor_rbm_rst = post.groom$rescor__rbms__rsts
)

df.cor.temp$model <- "+ NDVI"

df.cor <- bind_rows(df.cor, df.cor.temp)



######plot
library(tidyverse)
#df.cor.melt.g <- df.cor %>% gather("troops","groom",-model)
#ggplot(df.cor.melt.g, aes(x=troops, color=model,y=groom)) + geom_violin(aes(fill=model),alpha=0.3, color="black",draw_quantiles=c(0.025,0.5,0.975)) + geom_hline(yintercept = 0, linetype="dashed") + theme_classic()

df.cor.melt.g <- df.cor %>% pivot_longer(!last_col())
names(df.cor.melt.g) <- c("model","troops","value")

library(ggridges)
p.synch.groom <- ggplot(df.cor.melt.g %>% filter(model=="+ NDVI" | model=="+ Season" | model=="Base") , aes(y=factor(model,level=c('+ NDVI','+ Season','Base'   ) ),color=model,x=value)) + geom_density_ridges(aes(fill=model),alpha=0.73, color="black",scale = 4,rel_min_height = 0.01) + geom_hline(yintercept = 0, linetype="dashed") + theme_classic()

library("RColorBrewer")
p.synch.groom <- p.synch.groom + xlim(-1,1) + geom_vline(xintercept = 0, linetype="dashed") + theme(text = element_text(size = 16)) + facet_grid(vars(troops))+ theme(axis.text.y = element_text(hjust = 0)) + labs(y='')

p.synch.groom
```

```{r}
cowplot::plot_grid(
  p.synch.groom + xlim(-1,1) + geom_vline(xintercept = 0, linetype="dashed"),
  p.synch.groom.mod + xlim(-1,1),
  nrow=1, labels = c("a)","b)") )
```

### 3.2 Plots of the group responses to environmental change

Plot the response of strength to changes in NDVI
```{r plot ndvi str}
library(tidyverse)
model_to_use <- fitgp.synch.samp.pop.ite.males.season.ndvi


summary(str.tot.ndvi.ite$ndvi.s)

df.pred <- data.frame(yday.s= -1, ndvi.s=seq(-1.80592, 2.31502, length.out=100), rowID=1, pt.samp.s =0, rbm.samp.s =0, rst.samp.s =0 ,ite_pt_rst.s=0,ite_pt_rbm.s=0,ite_rbm_rst.s=0, males_PT.s=0,males_RBM.s=0, males_RST.s=0, size_PTs=0, size_RBMs=0,size_RSTs=0)

df.pred.pt<- as.data.frame(fitted(model_to_use,newdata = df.pred, resp = "pts", summary = F))
df.pred.rbm<- as.data.frame(fitted(model_to_use,newdata = df.pred, resp = "rbms", summary = F))
df.pred.rst<- as.data.frame(fitted(model_to_use,newdata = df.pred, resp = "rsts", summary = F))




#back scale each prediction
library(HDInterval)

df.pred.pt<-(df.pred.pt*sd(str.tot.ndvi.ite$pt, na.rm = T)) + mean(str.tot.ndvi.ite$pt, na.rm = T)
df.pred.pt.mean <- apply(df.pred.pt,2,mean)
df.pred.pt.hdi <- apply(df.pred.pt,2,hdi)
df.pred.pt.df <- data.frame(Estimate = (df.pred.pt.mean), lci = (df.pred.pt.hdi[1,]), uci = (df.pred.pt.hdi[2,]) )

df.pred.rst<-(df.pred.rst*sd(str.tot.ndvi.ite$rst, na.rm = T)) + mean(str.tot.ndvi.ite$rst, na.rm = T)
df.pred.rst.mean <- apply(df.pred.rst,2,mean)
df.pred.rst.hdi <- apply(df.pred.rst,2,hdi)
df.pred.rst.df <- data.frame(Estimate = (df.pred.rst.mean), lci = (df.pred.rst.hdi[1,]), uci = (df.pred.rst.hdi[2,]) )

df.pred.rbm<-(df.pred.rbm*sd(str.tot.ndvi.ite$rbm, na.rm = T)) + mean(str.tot.ndvi.ite$rbm, na.rm = T)
df.pred.rbm.mean <- apply(df.pred.rbm,2,mean)
df.pred.rbm.hdi <- apply(df.pred.rbm,2,hdi)
df.pred.rbm.df <- data.frame(Estimate = (df.pred.rbm.mean), lci = (df.pred.rbm.hdi[1,]), uci = (df.pred.rbm.hdi[2,]) )




#bind to data used to make predictions
df.pred.pt <- bind_cols(df.pred,df.pred.pt.df)
df.pred.rbm <- bind_cols(df.pred,df.pred.rbm.df)
df.pred.rst <- bind_cols(df.pred,df.pred.rst.df)

#add column to name troop
df.pred.pt$troop <- "pt"
df.pred.rbm$troop<- "rbm"
df.pred.rst$troop<- "rst"

#bind them
df.pred.all <-bind_rows(df.pred.pt,df.pred.rbm,df.pred.rst)

#melt
df.pred.melt <- df.pred.all %>% pivot_longer(cols=c(-troop,-yday.s,-ndvi.s,-rowID,-pt.samp.s,-rbm.samp.s,-rst.samp.s,-lci,-uci,-ite_pt_rst.s,-ite_pt_rbm.s,-ite_rbm_rst.s, -males_PT.s,-males_RBM.s, -males_RST.s, -size_PTs,-size_RSTs,-size_RBMs))

#plot it 
p.groom.ndvi<-ggplot(df.pred.melt, aes(x=ndvi.s, y=value, group=troop, ymin=lci, ymax=uci) ) + geom_ribbon(color=NA,aes(fill=troop),alpha=0.2)+ geom_line(aes(color=troop)) + theme_classic()
p.groom.ndvi
```

Plot the response of strength to changes in day of year
```{r plot seasonal str}

model_to_use <- fitgp.synch.samp.pop.ite.males.season.ndvi

summary(str.tot.ndvi.ite$yday.s)

df.pred <- data.frame(yday.s= seq(-1.6329, 1.7659, length.out=100), ndvi.s=0, rowID=1, pt.samp.s =0, rbm.samp.s =0, rst.samp.s =0 ,ite_pt_rst.s=0,ite_pt_rbm.s=0,ite_rbm_rst.s=0, males_PT.s=0,males_RBM.s=0, males_RST.s=0, size_PTs=0, size_RBMs=0,size_RSTs=0)

df.pred.pt<- as.data.frame(fitted(model_to_use,newdata = df.pred, resp = "pts",incl_autocor = F, summary=F))
df.pred.rbm<- as.data.frame(fitted(model_to_use,newdata = df.pred, resp = "rbms",incl_autocor = F, summary=F))
df.pred.rst<- as.data.frame(fitted(model_to_use,newdata = df.pred, resp = "rsts",incl_autocor = F, summary=F))


#back scale each prediction
library(HDInterval)

df.pred.pt<-(df.pred.pt*sd(str.tot.ndvi.ite$pt, na.rm = T)) + mean(str.tot.ndvi.ite$pt, na.rm = T)
df.pred.pt.mean <- apply(df.pred.pt,2,mean)
df.pred.pt.hdi <- apply(df.pred.pt,2,hdi)
df.pred.pt.df <- data.frame(Estimate = (df.pred.pt.mean), lci = (df.pred.pt.hdi[1,]), uci = (df.pred.pt.hdi[2,]) )

df.pred.rst<-(df.pred.rst*sd(str.tot.ndvi.ite$rst, na.rm = T)) + mean(str.tot.ndvi.ite$rst, na.rm = T)
df.pred.rst.mean <- apply(df.pred.rst,2,mean)
df.pred.rst.hdi <- apply(df.pred.rst,2,hdi)
df.pred.rst.df <- data.frame(Estimate = (df.pred.rst.mean), lci = (df.pred.rst.hdi[1,]), uci = (df.pred.rst.hdi[2,]) )

df.pred.rbm<-(df.pred.rbm*sd(str.tot.ndvi.ite$rbm, na.rm = T)) + mean(str.tot.ndvi.ite$rbm, na.rm = T)
df.pred.rbm.mean <- apply(df.pred.rbm,2,mean)
df.pred.rbm.hdi <- apply(df.pred.rbm,2,hdi)
df.pred.rbm.df <- data.frame(Estimate = (df.pred.rbm.mean), lci = (df.pred.rbm.hdi[1,]), uci = (df.pred.rbm.hdi[2,]) )


#bind to data used to make predictions
df.pred.pt <- bind_cols(df.pred,df.pred.pt.df)
df.pred.rbm <- bind_cols(df.pred,df.pred.rbm.df)
df.pred.rst <- bind_cols(df.pred,df.pred.rst.df)

#add column to name troop
df.pred.pt$troop <- "pt"
df.pred.rbm$troop<- "rbm"
df.pred.rst$troop<- "rst"

#bind them
df.pred.all <-bind_rows(df.pred.pt,df.pred.rbm,df.pred.rst)

#melt
df.pred.melt <- df.pred.all %>% pivot_longer(cols=c(-troop,-yday.s,-ndvi.s,-rowID,-pt.samp.s,-rbm.samp.s,-rst.samp.s,-lci,-uci,-ite_pt_rst.s,-ite_pt_rbm.s,-ite_rbm_rst.s, -males_PT.s,-males_RBM.s, -males_RST.s, -size_PTs,-size_RSTs,-size_RBMs))

#plot it 
p.groom.season<-ggplot(df.pred.melt, aes(x=yday.s, y=value, group=troop, ymin=lci, ymax=uci) ) + geom_ribbon(color=NA,aes(fill=troop),alpha=0.2)+ geom_line(aes(color=troop))  + theme_classic()

p.groom.season
```

```{r plot ndvi modularity}
summary(str.tot.ndvi.ite$ndvi.s)

df.pred <- data.frame(yday.s= 0, ndvi.s=seq(-1.80592, 2.31502, length.out=100), rowID=1, pt.samp.s =0, rbm.samp.s =0, rst.samp.s =0, size_PT.s=0,size_RBM.s=0,size_RST.s=0,ite_pt_rbm.s=0,ite_pt_rst.s=0,ite_rbm_rst.s=0, males_PT.s=0,males_RBM.s=0,males_RST.s=0)

df.pred.pt<- as.data.frame(fitted(fit.synch.mod.samp.pop.males.ite.season.ndvi,newdata = df.pred, resp = "pts",incl_autocor = F, summary = F))
df.pred.rbm<- as.data.frame(fitted(fit.synch.mod.samp.pop.males.ite.season.ndvi,newdata = df.pred, resp = "rbms",incl_autocor = F, summary = F))
df.pred.rst<- as.data.frame(fitted(fit.synch.mod.samp.pop.males.ite.season.ndvi,newdata = df.pred, resp = "rsts",incl_autocor = F, summary = F))


#back scale each prediction
library(HDInterval)

df.pred.pt<-(df.pred.pt*sd(mod.tot.ite.ndvi$pt, na.rm = T)) + mean(mod.tot.ite.ndvi$pt, na.rm = T)
df.pred.pt.mean <- apply(df.pred.pt,2,mean)
df.pred.pt.hdi <- apply(df.pred.pt,2,hdi)
df.pred.pt.df <- data.frame(Estimate = (df.pred.pt.mean), lci = (df.pred.pt.hdi[1,]), uci = (df.pred.pt.hdi[2,]) )

df.pred.rst<-(df.pred.rst*sd(mod.tot.ite.ndvi$rst, na.rm = T)) + mean(mod.tot.ite.ndvi$rst, na.rm = T)
df.pred.rst.mean <- apply(df.pred.rst,2,mean)
df.pred.rst.hdi <- apply(df.pred.rst,2,hdi)
df.pred.rst.df <- data.frame(Estimate = (df.pred.rst.mean), lci = (df.pred.rst.hdi[1,]), uci = (df.pred.rst.hdi[2,]) )

df.pred.rbm<-(df.pred.rbm*sd(mod.tot.ite.ndvi$rbm, na.rm = T)) + mean(mod.tot.ite.ndvi$rbm, na.rm = T)
df.pred.rbm.mean <- apply(df.pred.rbm,2,mean)
df.pred.rbm.hdi <- apply(df.pred.rbm,2,hdi)
df.pred.rbm.df <- data.frame(Estimate = (df.pred.rbm.mean), lci = (df.pred.rbm.hdi[1,]), uci = (df.pred.rbm.hdi[2,]) )

#bind to data used to make predictions
df.pred.pt <- bind_cols(df.pred,df.pred.pt.df)
df.pred.rbm <- bind_cols(df.pred,df.pred.rbm.df)
df.pred.rst <- bind_cols(df.pred,df.pred.rst.df)

#add column to name troop
df.pred.pt$troop <- "pt"
df.pred.rbm$troop<- "rbm"
df.pred.rst$troop<- "rst"

#bind them
df.pred.all <-bind_rows(df.pred.pt,df.pred.rbm,df.pred.rst)

#melt
df.pred.melt <- df.pred.all %>% pivot_longer(cols=c(-troop,-yday.s,-ndvi.s,-rowID,-pt.samp.s,-rbm.samp.s,-rst.samp.s,-lci,-uci, -size_PT.s,-size_RBM.s,-size_RST.s,-ite_pt_rbm.s,-ite_pt_rst.s,-ite_rbm_rst.s, -males_PT.s,-males_RBM.s,-males_RST.s))

#plot it 
p.mod.ndvi<-ggplot(df.pred.melt, aes(x=ndvi.s, y=value, group=troop, ymin=lci, ymax=uci) ) + geom_ribbon(color=NA,aes(fill=troop),alpha=0.2)+ geom_line(aes(color=troop)) + theme_classic()
p.mod.ndvi
```



```{r plot seasonal modularity with backscale}
summary(mod.tot.ite.ndvi$yday.s)

df.pred <- data.frame(yday.s= seq(-1.6329, 1.7659, length.out=100), ndvi.s=0, rowID=1, pt.samp.s =0, rbm.samp.s =0, rst.samp.s =0, size_PT.s=0,size_RBM.s=0,size_RST.s=0,ite_pt_rbm.s=0,ite_pt_rst.s=0,ite_rbm_rst.s=0, males_PT.s=0,males_RBM.s=0,males_RST.s=0 )

df.pred.pt<- as.data.frame(fitted(fit.synch.mod.samp.pop.males.ite.season.ndvi,newdata = df.pred, resp = "pts",incl_autocor = F, summary=FALSE))
df.pred.rbm<- as.data.frame(fitted(fit.synch.mod.samp.pop.males.ite.season.ndvi,newdata = df.pred, resp = "rbms",incl_autocor = F, summary=FALSE))
df.pred.rst<- as.data.frame(fitted(fit.synch.mod.samp.pop.males.ite.season.ndvi,newdata = df.pred, resp = "rsts",incl_autocor = F, summary=FALSE))

#back scale each prediction
library(HDInterval)

df.pred.pt<-(df.pred.pt*sd(mod.tot.ite.ndvi$pt, na.rm = T)) + mean(mod.tot.ite.ndvi$pt, na.rm = T)
df.pred.pt.mean <- apply(df.pred.pt,2,mean)
df.pred.pt.hdi <- apply(df.pred.pt,2,hdi)
df.pred.pt.df <- data.frame(Estimate = (df.pred.pt.mean), lci = (df.pred.pt.hdi[1,]), uci = (df.pred.pt.hdi[2,]) )

df.pred.rst<-(df.pred.rst*sd(mod.tot.ite.ndvi$rst, na.rm = T)) + mean(mod.tot.ite.ndvi$rst, na.rm = T)
df.pred.rst.mean <- apply(df.pred.rst,2,mean)
df.pred.rst.hdi <- apply(df.pred.rst,2,hdi)
df.pred.rst.df <- data.frame(Estimate = (df.pred.rst.mean), lci = (df.pred.rst.hdi[1,]), uci = (df.pred.rst.hdi[2,]) )

df.pred.rbm<-(df.pred.rbm*sd(mod.tot.ite.ndvi$rbm, na.rm = T)) + mean(mod.tot.ite.ndvi$rbm, na.rm = T)
df.pred.rbm.mean <- apply(df.pred.rbm,2,mean)
df.pred.rbm.hdi <- apply(df.pred.rbm,2,hdi)
df.pred.rbm.df <- data.frame(Estimate = (df.pred.rbm.mean), lci = (df.pred.rbm.hdi[1,]), uci = (df.pred.rbm.hdi[2,]) )

#bind to data used to make predictions
df.pred.pt <- bind_cols(df.pred,df.pred.pt.df)
df.pred.rbm <- bind_cols(df.pred,df.pred.rbm.df)
df.pred.rst <- bind_cols(df.pred,df.pred.rst.df)

#add column to name troop
df.pred.pt$troop <- "pt"
df.pred.rbm$troop<- "rbm"
df.pred.rst$troop<- "rst"

#bind them
df.pred.all <-bind_rows(df.pred.pt,df.pred.rbm,df.pred.rst)

#melt
df.pred.melt <- df.pred.all %>% pivot_longer(cols=c(-troop,-yday.s,-ndvi.s,-rowID,-pt.samp.s,-rbm.samp.s,-rst.samp.s,-lci,-uci, -size_PT.s,-size_RBM.s,-size_RST.s,-ite_pt_rbm.s,-ite_pt_rst.s,-ite_rbm_rst.s, -males_PT.s,-males_RBM.s,-males_RST.s))

#plot it 
p.mod.season<-ggplot(df.pred.melt, aes(x=yday.s, y=value, group=troop, ymin=lci, ymax=uci) ) + geom_ribbon(color=NA,aes(fill=troop),alpha=0.2)+ geom_line(aes(color=troop)) + theme_classic() 

p.mod.season
```





Plot together
```{r}
cowplot::plot_grid(p.groom.ndvi + theme_classic(),
                   p.groom.season+ theme_classic(),
                   p.mod.ndvi+ theme_classic(),
                   p.mod.season+ theme_classic(),
                   nrow=2, labels = c("a)","b)","c)","d)") )
```
